Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network \\ \begin{large} Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity \end{large}

### 2016-12-02 draft.tex
.

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{../../plots/power_spec/power_spectrum_analytic.png}
\end{center}
\caption{Power Spectrum of $\mathrm{\langle V_t \rangle}$ (blue) and analytic predictions based on Equation \eqref{Pow_Spec_Theta_Final} for different time constants of spike rate adaption. Red curve is a fit by tweaking $\tau_m$,$\alpha$ and the overall amplitude of \eqref{Pow_Spec_Theta_Final}.}
\label{Pow_Spec_Theta_vs_Analytic}
\end{figure}

>>>>

Figure \ref{Pow_Spec_Theta_vs_Analytic} shows the result. Apart from $\mathrm{\tau_r = 20\,ms}$, the prediction underestimates the preferred frequency of oscillations and the overall amplitude.   
\includegraphics[width=0.8\textwidth]{../../plots/power_spec/power_spectrum_analytic.png}
\caption{Power Spectrum of $\mathrm{\langle V_t \rangle}$ (blue) and analytic predictions based on Equation \eqref{Pow_Spec_Theta_Final} for different time constants of spike rate adaption. Red curve is a fit by tweaking $\tau_r$,$\alpha$ and the overall amplitude of \eqref{Pow_Spec_Theta_Final}. The fit returned $\mathrm{\tau_r=54\,ms}$, $\mathrm{\alpha=-1.02\,Hz/mV}$ and a correction of amplitude by a factor of $\mathrm{13.1}$.}
\label{Pow_Spec_Theta_vs_Analytic}
As a reference, we fitted equation \eqref{Pow_Spec_Theta_Final} to the simulation result by means of $\mathrm{\tau_r}$, $\mathrm{\alpha}$ and an additional multiplicative correction of amplitude (dashed line in Figure \ref{Pow_Spec_Theta_vs_Analytic}). The result for $\mathrm{\tau_r=54\,ms}$ is in line with our prediction that the firing rate adaption of the entire network should be slower than the membrane constant $\mathrm{\tau_m=20\,ms}$. The underestimation of preferred frequency strongly depends on the slope of the linear rate-threshold relation: a steeper slope results in faster oscillations and vice versa. While the fit seen in Figure \ref{thresh_r_linfit} resulted in $\mathrm{\alpha=-0.79\,Hz/mV}$, the fit in Figure \ref{Pow_Spec_Theta_vs_Analytic} returned $\mathrm{\alpha=-1.02\,Hz/mV}$. This discrepancy can be at least partially explained by the fact that the linear regression overestimates the importance of a number of outliers in the range of $\mathrm{\langle V_t \rangle > 54\,mV}$, resulting in a slightly too shallow negative slope. However, excluding these data points from the fit still resulted in a shallower slope of $\mathrm{\alpha=-0.85\,Hz/mV}$.
